Cosmic web alignments with the shape, angular momentum and peculiar velocities of dark matter halos

### 2014-02-11 paper/main.tex
starting the conclusions

@@

Figure \ref{fig:interweb} shows the results of the inter-web alignment
as a function of halo mass. It clearly stands out that the
eigenvectors are aligned for low mass halos but are close perpendicular to
each other at the location of the most massive halos. There is a
transition scale around $(10^{11.5}-10^{12.5})$\hMsun depending on the
grid resolution. The coarse grid $(256^3)$shows the transition at higher masses
than the fine grid $(512^3)$.

For both resolutions, the halos more massiven than $10^{13}$\hMsun are
locate in regions where the fastest momentum-weighted collapse
direction (defined by the V-web) is perpendicular to the direction
where the tidal compression is the highest.

The fact that this trend is less evident at low resolution and low
masses, hints that the flip is actually related to the overdensity
values, i.e. to the degree of non-linearity, in the corresponding
spatial scales.

@@

>>>>

Perhaps the most striking result so far is that the two webs give
different results for the alignment of massive halos. This is not
completely unexpected given that the two algorithms are based on
different physical premises to obtain the directions defining the
eigenvectors. However, we investigate the origin of the different
alignment statistics by studying the inter-web alignment.

Figure \ref{fig:interweb} shows the values for $\muavg$ between the
two $\vec{e}_1$ eigenvectors in the Tweb and the Vweb.  The Figure
shows that there is an alignment, $\muavg\approx 1.0$, for low mass
halos and an antialignment, $\muavg\approx 0.2$ for massive.

The transitional scale is located around $(10^{11.5}-10^{12.5})$\hMsun
depending on the grid resolution. The coarse grid $(256^3)$ shows the
transition at higher masses than the fine grid $(512^3)$.   We also
note that the alignment is weaker in the finer grid, ($\muavg\approx
0.7$) than in the coarser grid ($\muavg\approx1.0$).

These two facts (alignment at low masses and low grid resolution)
points towards an explanation in terms of the  linear / non-linear
growth of structure. When the alignment is present on linear scales
the divergence of the velocity field is proportional to the
overdensity, i.e. the trace of the shear field is proportional to the
trace of the tidal field.

On the scale where the halos more massiven than $10^{13}$\hMsun are
located, the relationshop between the velocity shear and the tidal
field changes. There, the fastest momentum-weighted collapse direction
(defined by the V-web) is perpendicular to the direction where the
tidal compression is the highest.

@@

@@

We quantify the alignments in two complementary ways. The first one
measures the fraction of halos in a poulation that is preferentially
aligned with either one of the eigenvectors $\vec{e}_1$, $\vec{e}_2$
or $\vec{e}_3$. The second method measures the average value of the
angle between an eigenvector and the quantity of interest. These two
measurements give us a complete picture for the different degrees of
alignment in the cosmic web.

We find that the strongest alignment occurs for the halo shape with
respect to the Tweb. In this case the halos tend to align with the
third eigenvector, $\vec{e}_3$, meaning that they lie along filaments
and walls. This trend is gets stronger as the halo mass
increases and agrees with all the results published so far. Instead,
for the Vweb, there is only an antialignment for halos more massive
than $10^{12}$\hMsun, a result that is presented here for the first
time.

A much weaker alignment signal is present for the angular momentum. In
the Tweb only the most massive halos $>10^{12}$\hMsun are antialigned
with respect to the filaments, while for the Vweb the massive halos
are alignment with sheets. These results broadly agree with the
published literature. Nevertheless, in the same publications there is an
alignment/anti-alignment signal reported at lower halo masses
$<10^{12}$\hMsun that we do not detect in our measurements.

A new result from our study is the alignment for the peculiar
velocities. Here we find a relatively strong signal of alignment along
the direction defined by the third eigenvector and perpendicular to
the first. This signal is very strong in the Tweb for all masses below
$<10^{13}$\hMsun. This can be interpreted as a flow parallel to walls
and filaments. In the case of the Vweb similar signal, albeit weaker,
is present only for the low mass halos $<10^{12}$\hMsun.

The different behaviour for the alignments of massive halos in the
Tweb and the Vweb was tracked to a corresponding anti-alignment
between the eigenvectors in the two webs.
